### 2022-01-31 preprint.tex
Performance-Based Evaluation

\subsection{Safe Join}

@@

\begin{lstlisting}
dependent val schema1 = Cons("age", Cons("name", Nil()))
dependent val schema2 = Cons("name", Cons("unit", Nil()))
dependent val table1  = Table(schema1, (*\text{\dots}*))
dependent val table2  = Table(schema2, (*\text{\dots}*))
dependent val joined  = table1.join(table2, "name")
joined: { Table(Cons("name", Cons("age", Cons("unit", Nil()))), choose[DataFrame]) }
\end{lstlisting}

>>>>

\subsection{Safe Join}
\label{sec:safe-join}

@@

\begin{lstlisting}
dependent val schema1 = Cons("age", Cons("name", Nil()))
dependent val schema2 = Cons("name", Cons("unit", Nil()))
dependent val table1  = Table(schema1, (*\text{\dots}*))
dependent val table2  = Table(schema2, (*\text{\dots}*))
dependent val joined  = table1.join(table2, "name")
joined: { Table(
            Cons("name", Cons("age", Cons("unit", Nil()))),
            choose[DataFrame]) }
\end{lstlisting}
